Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-04-25 awipev-CO2.Rmd
lost of several data due to change with sal_insitu_ctd and temp_insitu_ctd with 1m/3m/5m/7m/9m

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  # dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
  #        AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
  #        #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
  #        #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
  #        ) %>%
  # variables passed through despike with "-filtered" have been renamed without sufix.
  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, temp_sf = T_seaF)
d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))

@@

```{r Sal filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
#### filter salinities above 28
d_all <- d_all%>%
  dplyr::mutate( sal_fb = ifelse(sal_fb <28, NA, sal_fb),
                 sal_insitu_ctd = ifelse(sal_insitu_ctd <28, NA, sal_insitu_ctd))
 d_all <- d_all%>%
  dplyr::mutate(sal_insitu_ctd = ifelse(datetime > "2019-12-26 00:00:00", NA, sal_insitu_ctd))

########### Binding sal_fb + sal_insitu if we get gaps in sal_insitu = call this new column = sal_mix ########### 
d_all <- d_all %>%
  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, 
                               ifelse (pressure_insitu_ctd >=8 ,sal_insitu_ctd, NA )))
### remove sal_mix data that seem to be to high compared to sal_fb
  d_all <- d_all%>%
  dplyr::mutate(sal_mix = ifelse(datetime > "2018-03-09 00:00:00" & datetime < "2018-04-13 18:00:00" , NA, 
                          ifelse(datetime > "2018-05-21 19:00:00" & datetime < "2018-05-24 17:00:00" , NA,
                          ifelse(datetime > "2018-05-29 15:00:00" & datetime < "2018-06-03 13:00:00" , NA,
                          ifelse(datetime > "2018-06-16 06:00:00" & datetime < "2018-06-21 05:00:00" , NA,
                          ifelse(datetime > "2019-12-02 08:00:00" & datetime < "2019-12-03 08:00:00" , NA,
                          ifelse(datetime > "2019-12-09 07:00:00" & datetime < "2019-12-09 10:00:00" , NA, 
                          ifelse(datetime > "2019-12-09 15:00:00" & datetime < "2019-12-09 18:00:00" , NA,
                          ifelse(datetime > "2019-12-10 14:00:00" & datetime < "2019-12-10 18:00:00", NA, sal_mix)))))))))

### creation of column sal_insitu_sup_8m 
   d_all <- d_all%>%
     dplyr::mutate(sal_insitu_sup_8m = ifelse(pressure_insitu_ctd >=8, sal_insitu_ctd, NA))

@@

```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
###### Binding temp_insitu_11m + temp_insitu_ctd if we get gaps in temp_insitu_11m = call this new column = temp_mix ####### 
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, 
                               ifelse (pressure_insitu_ctd >=8 ,temp_insitu_ctd, NA )))

# qf added 
d_all <- d_all %>% 
  dplyr::mutate(
    temp_fb_qf = ifelse(
      State_Zero >= 1 | State_Flush >= 1 |
        pco2_raw < 100 | pco2_raw > 450 |
        Time >= "00:00:00" & Time <= "01:30:00" |
        Time >= "12:00:00" & Time <= "13:00:00" |
        datetime == "2017-03-22 08:00:00" ,
      4,
      1
    ),
    pco2_raw = ifelse(pco2_raw_qf == 4 , NA, pco2_raw),
    pco2_corr_qf = ifelse(
      State_Zero >= 1 | State_Flush >= 1 |
        pco2_corr < 100 | pco2_corr > 450 |
        Time >= "00:00:00" & Time <= "01:30:00" |
        Time >= "12:00:00" & Time <= "13:00:00" |
        datetime >= "2017-03-10 08:00:00" &
        datetime < "2017-03-21 20:00:00",
      4,
      1
    ),
    pco2_corr = ifelse(pco2_corr_qf == 4 , NA, pco2_corr)
  )
```

@@

# add sal_fb + sal_insitu_ctd + temp_fb + temp_insitu_ctd from d_all into d, to use pHinsi
# use the closest time to add them
closest <- which.closest(d$datetime, d_all$datetime) # closest date and time
d$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
d$closest_datetime[abs(d$datetime - d_all$datetime[closest]) > 30*60] <- NA
# create closest_datetime in d_all (copy of datetime)
d_all$closest_datetime <- d_all$datetime
d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, sal_insitu_ctd, temp_mix, temp_insitu_ctd, temp_insitu_11m, sal_mix )), by="closest_datetime")

# Conversion of spectro pH to insitu mix T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet) & !is.na(sal_insitu_ctd) & !is.na(temp_mix) )
pH_seafet <- pH_seafet %>%
  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_mix, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_mix,Pt=0,Sit=0))

@@

sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd)

@@

      dySeries("sal_insitu_ctd", color = "blue", strokeWidth = 0, label = "sal_insitu_ctd") %>%

@@

temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu_ctd)

@@

      dySeries("temp_insitu_ctd", color = "blue", strokeWidth = 0, label = "temp_insitu_ctd") %>%

@@

### **Sal FB / Sal CTD > 8 m **

@@

fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd >=8),  sal_fb ~ sal_insitu_ctd , nperm = 99)

```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd >=8),  sal_fb ~ sal_insitu_ctd , nperm = 99)

@@

p_sal_fb_ctd<-  ggplot(d_all%>%dplyr::filter(pressure_insitu_ctd >=8),aes(x=sal_insitu_ctd, y= sal_fb))+
  geom_point( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  #geom_line(aes(x = sal_fb, y = sal_fb), linetype = "dashed") +
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + #
  coord_fixed(ratio = 1 )+
 #  scale_colour_discrete(guide="none") +
  labs( x="Salinity CTD > 8 m", y="Salinity FB ", color = "Months") +theme_bw()

@@

d_all$diff_sal_fb_insitu <- d_all$sal_insitu_ctd - d_all$sal_fb
mean_diff_sal_fb_insitu <- round(mean(d_all$diff_sal_fb_insitu, na.rm = TRUE), digits = 2)
sd_diff_sal_fb_insitu <- round(sd(d_all$diff_sal_fb_insitu, na.rm = TRUE), digits = 2)

@@

```{r Sal plot, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
seafet_contros_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd, sal_fb, sal_mix)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="Salinities", ylab="PSU") %>%
dySeries("sal_insitu_ctd", label = "sal_insitu_ctd", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
dySeries("sal_fb", label = "sal_fb", color ="blue",axis= "y2", strokeWidth=0, pointSize=4) %>%
dySeries("sal_mix", label = "sal_mix", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
#dySeries("pressure_insitu_ctd", label = "pressure_insitu_ctd", color ="black", strokeWidth=0, pointSize=2) %>%
  dyLegend(show = "onmouseover")   %>%
  #dyAxis( "y2",valueRange = c(-3, 36))%>%
  #dyAxis( "y2",valueRange = c(25, 36))%>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)
```

The mean difference between salinity FB and in situ is: `r mean_diff_sal_fb_insitu` ± `r sd_diff_sal_fb_insitu` PSU.

@@

- 1 SBE45 inside the Ferrybox (temp_fb)
- 5 CTD > 8 meters depth (temp_insitu_ctd)
- 1 fixed at 11 meters depth (temp_insitu_11m)

@@

fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd >=8),  temp_insitu_11m ~ temp_insitu_ctd , nperm = 99)

@@

fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd >=8),  temp_insitu_11m ~ temp_insitu_ctd , nperm = 99)

p<-  ggplot(d_all,aes(x=temp_insitu_ctd, y= temp_insitu_11m, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("T CTD > 8 m vs T 11 m","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="T CTD > 8 m", y="T 11 m ", color = "Months")  +theme_bw()
print(p)

d_all$diff_T_ctd_11m <- d_all$temp_sf - d_all$temp_insitu_ctd
mean_diff_T_ctd_11m <- round(mean(d_all$diff_T_ctd_11m, na.rm = TRUE), digits = 2)
sd_diff_T_ctd_11m <- round(sd(d_all$diff_T_ctd_11m, na.rm = TRUE), digits = 2)
```

@@

####
## calculation of E0INT25/E0EXT25 ##
##     new sf_calib function      ##
####
calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_mix,
                          calT = d_all$temp_insitu_ctd, calSal = d_all$sal_insitu_ctd )
# put number of deployment 
calib_spectro$deployment_sf <- d_all$deployment_sf

@@

```{r seaFET pH calculation sf_calc, echo=FALSE,message= FALSE, warning=FALSE}
####
## calculation of the calibrated pH ##
##       new sf_calc function       ##
####
seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_insitu_ctd, calSal = d_all$sal_insitu_ctd)

@@

seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_mix,pHint_tot_sf, pHint_tot_sf_filtered, pH_s_sf_no_calb)
seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
dygraph(seafet_depth_xts, group = "depth", main="pH seaFET (ref + corrected + raw)", ylab="pHT") %>%
dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 3) %>%
dySeries("pHint_tot_sf_filtered", label = "pHint_tot_sf_filtered", color =  RColorBrewer::brewer.pal(3, "Dark2")[4], strokeWidth = 0, pointSize = 2) %>%
dySeries("ph_s_sf_temp_mix", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%

dySeries("pH_s_sf_no_calb", label = "pH spectro no calibration", color =  "black", pointShape = "triangle", strokeWidth = 0, pointSize = 6 ) %>%

  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#E0E0E0") %>%
  dyLegend(show = "auto")   %>%
  dyAxis("y2",valueRange = c(-2, 2)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

@@

```{r pHs comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# remove sf biofouling period
pH_sf <- d_all %>%
  dplyr::select(datetime, sal_insitu_ctd, temp_insitu_ctd, pHint_tot_sf)%>%
  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu_ctd), !is.na(sal_insitu_ctd)) %>%
  dplyr::filter(datetime< "2018-01-01" | datetime> "2018-02-03")
pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu_ctd, Pinsi=11/10, S=pH_sf$sal_insitu_ctd, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

@@

### **Calculated / seaFET pHs**
```{r pHs comparaison sf calc, echo=FALSE, message= FALSE, warning=FALSE}
# SEAFET vs CALC
fit <- lmodel2(data = d_all,  pH_calc_norm4 ~ pHint_tot_sf_norm4 , nperm = 99)

>>>>

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  # dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
  #        AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
  #        #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
  #        #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
  #        ) %>%
  # variables passed through despike with "-filtered" have been renamed without sufix.
  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, ph_dur = ph_dur_filtered, temp_sf = T_seaF)
d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))

@@

```{r Sal filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}

########### Binding sal_fb + sal_insitu if we get gaps in sal_insitu = call this new column = sal_mix ########### 
d_all <- d_all %>%
  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, sal_insitu_ctd_9m))

# ### remove sal_mix data that seem to be to high compared to sal_fb
#   d_all <- d_all%>%
#   dplyr::mutate(sal_mix = ifelse(datetime > "2018-03-09 00:00:00" & datetime < "2018-04-13 18:00:00" , NA, 
#                           ifelse(datetime > "2018-05-21 19:00:00" & datetime < "2018-05-24 17:00:00" , NA,
#                           ifelse(datetime > "2018-05-29 15:00:00" & datetime < "2018-06-03 13:00:00" , NA,
#                           ifelse(datetime > "2018-06-16 06:00:00" & datetime < "2018-06-21 05:00:00" , NA,
#                           ifelse(datetime > "2019-12-02 08:00:00" & datetime < "2019-12-03 08:00:00" , NA,
#                           ifelse(datetime > "2019-12-09 07:00:00" & datetime < "2019-12-09 10:00:00" , NA, 
#                           ifelse(datetime > "2019-12-09 15:00:00" & datetime < "2019-12-09 18:00:00" , NA,
#                           ifelse(datetime > "2019-12-10 14:00:00" & datetime < "2019-12-10 18:00:00", NA, sal_mix)))))))))

@@

```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
###### Binding temp_insitu_11m + temp_insitu_ctd if we get gaps in temp_insitu_11m = call this new column = temp_mix ####### 
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, temp_insitu_ctd_9m))
```

@@

# add sal_fb + sal_insitu_ctd + temp_fb + temp_insitu_ctd from d_all into d, to use pHinsi
# use the closest time to add them
closest <- which.closest(d$datetime, d_all$datetime) # closest date and time
d$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
d$closest_datetime[abs(d$datetime - d_all$datetime[closest]) > 30*60] <- NA
# create closest_datetime in d_all (copy of datetime)
d_all$closest_datetime <- d_all$datetime
d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, temp_mix, temp_insitu_11m, sal_mix )), by="closest_datetime")

# Conversion of spectro pH to insitu mix T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet) & !is.na(temp_mix) )
pH_seafet <- pH_seafet %>%
  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_mix, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_mix,Pt=0,Sit=0))

@@

sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m)

@@

dySeries("sal_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
dySeries("sal_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
dySeries("sal_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
dySeries("sal_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
dySeries("sal_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%

@@

temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_9m)

@@

      dySeries("temp_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
dySeries("temp_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
dySeries("temp_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
dySeries("temp_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
dySeries("temp_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%

@@

### **Sal FB / Sal CTD 9 m **

@@

fit <- lmodel2(data = d_all,  sal_fb ~ sal_insitu_ctd_9m , nperm = 99)

```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
fit <- lmodel2(data = d_all,  sal_fb ~ sal_insitu_ctd_9m , nperm = 99)

@@

p_sal_fb_ctd<-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
  geom_point( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  #geom_line(aes(x = sal_fb, y = sal_fb), linetype = "dashed") +
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + #
  coord_fixed(ratio = 1 )+
 #  scale_colour_discrete(guide="none") +
  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") +theme_bw()

@@

d_all$diff_sal_fb_insitu_9m <- d_all$sal_insitu_ctd_9m - d_all$sal_fb
mean_diff_sal_fb_insitu_9m <- round(mean(d_all$diff_sal_fb_insitu_9m, na.rm = TRUE), digits = 2)
sd_diff_sal_fb_insitu_9m <- round(sd(d_all$diff_sal_fb_insitu_9m, na.rm = TRUE), digits = 2)

@@

```{r Sal plot, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}

sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m, sal_mix, sal_fb)
sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD, all depths)", ylab="Salinity") %>%
dySeries("sal_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
dySeries("sal_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
dySeries("sal_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
dySeries("sal_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
dySeries("sal_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
  dySeries("sal_fb", color = "grey", strokeWidth = 0, label = "sal_fb") %>%

dySeries("sal_mix", color = "black", strokeWidth = 0, label = "sal_mix") %>%

      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyAxis("y",valueRange = c(30, 37)) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)
```

The mean difference between salinity FB and in situ is: `r mean_diff_sal_fb_insitu_9m` ± `r sd_diff_sal_fb_insitu_9m` PSU.

@@

- 1 SBE45 inside the Ferrybox (temp_fb)
- 5 CTD profiling (temp_insitu_ctd_1m - 3m - 5m - 7m - 9m)
- 1 fixed at 11 meters depth (temp_insitu_11m)

@@

fit <- lmodel2(data = d_all,  temp_insitu_11m ~ temp_insitu_ctd_9m , nperm = 99)

@@

fit <- lmodel2(data = d_all,  temp_insitu_11m ~ temp_insitu_ctd_9m , nperm = 99)

p<-  ggplot(d_all,aes(x=temp_insitu_ctd_9m, y= temp_insitu_11m, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("T CTD 9 m vs T 11 m","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="T CTD 9 m", y="T 11 m ", color = "Months")  +theme_bw()
print(p)

d_all$diff_T_ctd_11m <- d_all$temp_sf - d_all$temp_insitu_ctd_9m
mean_diff_T_ctd_11m <- round(mean(d_all$diff_T_ctd_11m, na.rm = TRUE), digits = 2)
sd_diff_T_ctd_11m <- round(sd(d_all$diff_T_ctd_11m, na.rm = TRUE), digits = 2)
```

@@

####
## calculation of E0INT25/E0EXT25 ##
##     new sf_calib function      ##
####
calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_mix,
                          calT = d_all$temp_insitu_ctd_9m, calSal = d_all$sal_insitu_ctd_9m )
# put number of deployment 
calib_spectro$deployment_sf <- d_all$deployment_sf

@@

```{r seaFET pH calculation sf_calc, echo=FALSE,message= FALSE, warning=FALSE}
####
## calculation of the calibrated pH ##
##       new sf_calc function       ##
####
seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_insitu_ctd_9m, calSal = d_all$sal_insitu_ctd_9m)

@@

seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_mix,pHint_tot_sf, pH_s_sf_no_calb)
seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
dygraph(seafet_depth_xts, group = "depth", main="pH seaFET (ref + corrected + raw)", ylab="pHT") %>%
dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 3) %>%
dySeries("ph_s_sf_temp_mix", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
dySeries("pH_s_sf_no_calb", label = "pH spectro no calibration", color =  "black", pointShape = "triangle", strokeWidth = 0, pointSize = 6 ) %>%
dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#E0E0E0") %>%
  dyLegend(show = "auto")   %>%
  dyAxis("y2",valueRange = c(-2, 2)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

@@

```{r pHs comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# remove sf biofouling period
pH_sf <- d_all %>%
  dplyr::select(datetime, sal_insitu_ctd_9m , temp_insitu_ctd_9m, pHint_tot_sf)%>%
  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu_ctd_9m), !is.na(sal_insitu_ctd_9m)) %>%
  dplyr::filter(datetime< "2018-01-01" | datetime> "2018-02-03")
pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_9m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_9m, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

@@

### **Calculated / seaFET pHs**
```{r pHs comparaison sf calc, echo=FALSE, message= FALSE, warning=FALSE}
# SEAFET vs CALC
# fit <- lmodel2(data = d_all,  pH_calc_norm4 ~ pHint_tot_sf_norm4 , nperm = 99)
# 
# psf_calc_norm_text <-  ggplot(d_all,aes(x=pHint_tot_sf_norm4, y= pH_calc_norm4, label = month))+
#   geom_text( aes(color=factor(month))) + 
#   scale_color_discrete(guide = "none")+
#  geom_abline(slope=1, intercept =0, linetype = "dashed") +
#   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
#   labs(title = paste("pH calculated vs pH seaFET, normalized at 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
#                      "; Intercept =", signif(fit$regression.results[2,2], 3),
#                      "; Slope =", signif( fit$regression.results[2,3], 3),
#                      "; P =", signif(fit$P.param, 3))) +
#   theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
#     coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
#   labs(x="pH seaFET, 4°C", y="pH calculated, 4°C ", color = "Months") + theme_bw() 
# psf_calc_norm_text
